\chapter*{\uppercase{ABSTRACT}}
\addcontentsline{toc}{section}{\bfseries \uppercase{Abstract}}

The issue of Technical debt has been a subject of controversy for sometime now, Technical debt as such is not harmful for a software project but it is essential to identify such technical debts in the project as soon as possible because the later you find the more the debt increases and at last it becomes unbearable to pay back similar to the financial debts in our real life.
\par There have been many methods suggested to identify technical debts in the project like Code Smells, Source Code Analysis, Comment analysis etc., In this project we have come with a new and novel way to identify these technical debts and it is by going through the bug reports of that particular software. On applying text processing to the bug reports we have classified a bug report as either a technical report or a non-technical report. Thus the developers and testers can concentrate in detail on the bugs that were marked as technical.
\par For this project we have concentrated on the Chromium Project, it is a open source project from Google. The bug can be filed by anyone using a software called Monorail. We have scraped 700 of these issues for now as our dataset and given this to software engineering experts who classified these bugs as either technical or non-technical. This is the dataset using which we have experimented with various Text Classification methods. In essential we are using NLP methods to analyse and understand the issues and then classify it as either Technical or Non-Technical.
\par \emph{Keywords}: Technical Debt, Chromium Project, Code Smells, NLP.
